---
title: "Raw Data inspectation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## loading data for raw data inspection
distributors_df <- read.csv("./gen/data-preparation/input/distributors.csv", sep = ",")
producers_df <- read.csv("./gen/data-preparation/input/producers.csv", sep = ",")
content_df <- read.csv("./gen/data-preparation/input/content.csv", sep = ",")
reviews_df <- read.csv("./gen/data-preparation/input/reviews.csv", sep = ",")
releases_df<- read.csv("./gen/data-preparation/input/releases.csv", sep = ";")

##needed packages
library(dplyr)
```

#Raw data inspection

#Distributors
## Explaining the variables
For every unique imdb id there can be found a unique distributor name, type and country. An imdb id can have multiple names, types and country's connected to it. We also see the start year and end year of the distributor, where there is a minimum and maximum. The average start year is 2013 and end year is 2014. There are 403 missing cases here.

```{r}
summary(distributors_df)
```
## By most country

We see that the country where most shows/movies get produced is the USA with follow up of the Netherlands. Worldwide is also high up and means that it is distributed by more than 1 country.

```{r }
distributors_df%>%
  group_by(distributor_country)%>%
  summarise(n=n())%>%
  arrange(desc(n))
```
## by type 

We see that theatrical is the most distributed by type with following of tv and video. One unique imdb id can have more than one distributor type, so it is possible they have a theatrical distribution and later is also distributed on multiple other platforms.

```{r}
distributors_df%>%
  group_by(distributor_type)%>%
  summarise(n=n())%>%
  arrange(desc(n))
```
#by name

We see there is strong variation in the company who distributed the tv-show or movie with Netflix clearly on top with the most distribution.

```{r}
distributors_df%>%
  group_by(distributor_name)%>%
  summarise(n=n())%>%
  arrange(desc(n))
```
#beginning and end year netflix

A follow up on the data above we see that the first Netflix distribution was in 1997 and already in progress for the latest distribution title in 2023.

```{r}

distributors_df%>%
  filter(distributor_name== 'Netflix')%>%
  summarise(min=min(distributor_start_year, na.rm= TRUE), 
            max=max(distributor_end_year, na.rm= TRUE))

distributor_with_deletion<-distributors_df%>%
  filter(!(distributor_name== 'Netflix'& distributor_start_year< 1997))

distributor_with_deletion%>%
  filter(distributor_name== 'Netflix')%>%
  summarise(min=min(distributor_start_year, na.rm= TRUE), 
            max=max(distributor_end_year, na.rm= TRUE))

```

# Producers
## Explaining the variables

We have 5649 unique imdb id's which all can have multiple producers.

```{r producers}
summary(producers_total)
```

# by producer 
```{r}
producers_df%>%
  filter(grepl('Netflix', producer))%>%
  summarise(n=n())
```

# Content
## explaning the variables

The content set consists of 4855 unique imdb id's which all have a title, duration, country and can have multiple stars and genres connected to them.

```{r}
summary(content_total)
```
##By most country

Here we see the country's where the most content is available.

```{r}
content_df%>%
  group_by(country)%>%
  summarise(n=n())%>%
  arrange(desc(n))
```
## by genre

The highest value in content by genre is comedy followed by documentary and drama.

```{r}
content_df%>%
  group_by(genres)%>%
  summarise(n=n())%>%
  arrange(desc(n))
```
## by most stars

Here we see the stars that play in the movie/tv shows ranked from high to low.

```{r}
content_df%>%
  filter(!(stars== "[]"))%>% 
  group_by(stars)%>%
  summarise(n=n())%>%
  arrange(desc(n))
```
# Reviews
## explaning the variables

In total there are 429.977 reviews that were collected. One unique imdb id can have multiple review ratings.

```{r}
summary(reviews_total)
```
##Missing values

Here we see that for every review writen there are no missing values for the date of writing and 17.519 missing values on the review rating given. So sometimes it is possible no rating was giving by people when writing the review.

```{r}
# get na
sum(reviews_df$review_rating== "")

sum(reviews_df$data== "")
  
```
## by imdb id 

Here we see for which imdb id the most reviews were writen, which can indicate the popularity of a show or movie.

```{r}

reviews_df%>%
  group_by(id)%>%
  summarise(n=n())%>%
  arrange(desc(n))
  
```
## by imdb id

The average reviews written for a show or movie is 98. We do see that the middle value of reviews written is 19 so there is a big spread in whether one show/movie has a lot of reviews and the other one has not. In later research this could point to how popular a show/movie is.

```{r}

reviews_df%>%
  group_by(id)%>%
  summarise(n=n())%>%
  summarise(median= median(n),
            mean= mean(n),
            sd= sd(n))
  


  
```
## by rating

The average rating of a show/movie is a 6.8.

```{r}
  
# get first number in rating
reviews_df$review_rating_num <- as.numeric(gsub("/.*", "", reviews_df$review_rating))

reviews_df%>%
  summarise(mean= mean(review_rating_num, na.rm= TRUE))
```

## Review Date

The first date where a review was written was in 1998 where the latest review written was on 2020-12-31 , so this was the latest point in collecting the review data.

```{r}

# set review date to actual date
reviews_df$review_data <- as.Date(reviews_df$review_data, "%d %B %Y")  

reviews_df%>%
  summarise(min=min(review_data, na.rm= TRUE), 
            max=max(review_data, na.rm= TRUE))

```

# Releases
## Explaining the variables

In the releases dataset for every unique imdb id we can find a tmdb id which contain the information about the release date of the show/movie the season numbers and episode numbers. Every id is split up in seasons en contains for that season a certain number of episodes.

```{r}
summary(releases_df)
```
## Number of seasons

The minimum amount of seasons is 1 where the maximum is 48, so this is probably an outlier. This because the average amount of seasons is 3.7 and the exact middle of the data is 2 seasons. The standard deviation tells us about the spread which is almost 5 so there is a big spread in the number of seasons per show.
```{r}

releases_df%>%
  summarise(min=min(season_number, na.rm= TRUE), 
            max=max(season_number, na.rm= TRUE),
            median= median(season_number,na.rm = TRUE),
            mean= mean(season_number, na.rm = TRUE),
            sd= sd(season_number, na.rm = TRUE))
```
## Number of episodes

Here we see the minimum number of episodes per id and the maximum number of episodes. The average number of episodes for a tv show is 40 while the middle of the data set contains 9 number of episodes. This means that there is a spread which we can see in the standard deviation which is 174.

```{r}

releases_df%>%
  summarise(min=min(episode_number, na.rm= TRUE), 
            max=max(episode_number, na.rm= TRUE),
            median= median(episode_number,na.rm = TRUE),
            mean= mean(episode_number, na.rm = TRUE),
            sd= sd(episode_number, na.rm = TRUE))
```
## Weekday Release

The most shows were released on a friday with the following of thursday. These are the most populair days when a show is released to the public.

```{r}
releases_df$release_date <- as.Date(releases_df$release_date, "%Y-%m-%d")

releases_df$weekdays<- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", 
    "Friday", "Saturday")[as.POSIXlt(releases_df$release_date)$wday + 1]

releases_df%>%
  group_by(weekdays)%>%
  summarise(n=n())%>%
  arrange(desc(n))

```



#missing data

## missing content data

In the content dataset we have no missing values for the title of a tv-show?movie. We do have missing values for the following: 852 missing for the duration of a show/movie, 3 country's missing in the set, 135 stars and 15 genres not found.

```{r}
# content 
sum(content_df$title == "")
sum(content_df$duration == "")
sum(content_df$country == "")
sum(content_df$stars == "[]")
sum(content_df$genres == "[]")
```
## Missing content distributors

In the distributors set we have no missing data in the distributor name, country and type. We do have missing values in the distributor start and end year which are respectively 403 each.

```{r}
# distributors
sum(distributors_df$distributor_name == "")
sum(distributors_df$distributor_country == "")
sum(distributors_df$distributor_type == "")
sum(is.na(distributors_df$distributor_start_year))
sum(is.na(distributors_df$distributor_end_year))
```
## Missing data producers

In the producers set we have 664 missing values which indicate that for 664 id's the producers is missing.

```{r}
# producers
sum(producers_df$producer == "[]")
```
## Missing data reviews

In the review dataset we miss in total 17.519 unique review ratings.

```{r}
# reviews
sum(reviews_df$review_data == "")
sum(reviews_df$review_rating== "")

```
## Missing data releases

In the releases dataset for every release of a show there are 2566 missing values for the season and episode number.

```{r}
# releases
sum(releases_df$release_date == "")
sum(is.na(releases_df$season_number))
sum(is.na(releases_df$episode_number))
```